---
title: "UN report on the relationship between gdp and life expectancy and co2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-packages}
library(tidyverse)

```


This report was prepared to the attention of the United Nations. It analyzes the relationship between a country's GDP, its life expectancy and CO2 emissions. Our goal is to determine to what degree a country’s economic strength or weakness may be related to its public health status and impact on climate pollution. We hypothesize that both life expectancy and CO2 emissions increase with a country's GDP.

```{r}
setwd("C:/Users/agh5/Desktop/un-report/un-report")
gapminder_1997 <- read_csv("gapminder_1997.csv")
```

```{r gdp-lifeExp-1997-[plot]}
#make plot of gdp x axis vs lifeexp y axis
ggplot(data = gapminder_1997) + 

  aes(x = gdpPercap, y = lifeExp, color=continent, size=pop/1000000) +

  geom_point() +

  labs(x = "GDP Per Capita", y = "Life Expectancy",

       title= "Do people in wealthy countries live longer?", size="Population (in millions)")

```

